abc

### 2024-08-18 randpython.qmd
abc

def genpolycoeff(plr=1,parm=["alpha", "x", "y"],solvd='alpha',eur=[0, 0, 0]):

@@

    sympy.var('alpha x y g h n m zeta Gamma lamda ui')

@@

    sum_eur = sum(eur)

@@

    if sum_eur == 0:
        exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
        polys = poly(exprc, sympify(solvd)).all_coeffs()

@@

        return ABCDE 

@@

                nrs = dxyz[solvd]-1

@@

```{pyodide-python}
genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y') 
genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y',eur=[1, 4, 2])[0]
```

>>>>

def genpolycoeff(equn="alpha=k0+k1*g+k2*h",solv='y',grd=0,parm=["alpha", "x", "y"],plr=1,eur=[1, 4, 2]):

@@

    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')

@@

@@

    if grd == 0:
        #exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
        ls, rs = equn.split('=')
        eqs = Eq(sympify(ls), sympify(rs))
        polys = poly(eqs.rhs - eqs.lhs, sympify(solv)).all_coeffs()

@@

        return ABCDE, 0, 0

@@

                nrs = dxyz[solv]-1

@@

```{pyodide-python}
#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")
#genpolycoeff(plr=1,parm=["alpha", "x", "y"], solv='y',grd=1,eur=[1, 4, 2])[0]
```
